### 2019-06-24 README.Rmd
fixed README.Rmd so code is ital

First we will use the \code{get_kegg} function access the KEGG REST API and download the data sets required to perform 
our downstream analysis. This function takes two arguments. The first, \code{species} is required and is the species of 
interest. Currently, *diffEnrich* supports three species, and the argument is a character string using the KEGG
code [REF](https://www.pnas.org/content/suppl/2008/09/11/0806162105.DCSupplemental/ST1_PDF.pdf): 
Homo sapiens (human), use 'hsa'; Mus musculus (mouse), use 'mmu', and Rattus norvegicus (rat), use 'rno'. The second,
\code{path} is also passed as a character string, and is the path of the directory in which the user would like to
write the data sets downloaded from the KEGG REST API. If the user does not provide a path, the data sets will 
be automatically written to the current working directory using the \code{here::here()} functionality. These data 
sets will be tab delimited files with a name describing the data, and for reproducibility the date they were generated
and the version of KEGG when the API was accessed. In addition to these flat files, \code{get_kegg} will also
create a named list with the three relavent KEGG data sets. The names of this list will describe the the data set.

@@

**Note:** Because it is assumed that the user might want to use the data sets generated by \code{get_kegg}, it is careful not to
overwrite data sets with exact names. \code{get_kegg} checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can of course generate 'same-day/same-version'
data sets in different directories if they so choose.

>>>>

First we will use the *get_kegg* function access the KEGG REST API and download the data sets required to perform 
our downstream analysis. This function takes two arguments. The first, 'species' is required and is the species of 
interest. Currently, *diffEnrich* supports three species, and the argument is a character string using the KEGG
code [REF](https://www.pnas.org/content/suppl/2008/09/11/0806162105.DCSupplemental/ST1_PDF.pdf): 
Homo sapiens (human), use 'hsa'; Mus musculus (mouse), use 'mmu', and Rattus norvegicus (rat), use 'rno'. The second,
'path' is also passed as a character string, and is the path of the directory in which the user would like to
write the data sets downloaded from the KEGG REST API. If the user does not provide a path, the data sets will 
be automatically written to the current working directory using the *here::here()* functionality. These data 
sets will be tab delimited files with a name describing the data, and for reproducibility, the date they were generated
and the version of KEGG when the API was accessed. In addition to these flat files, *get_kegg* will also
create a named list with the three relavent KEGG data sets. The names of this list will describe the the data set.

@@

**Note:** Because it is assumed that the user might want to use the data sets generated by *get_kegg*, it is careful not to
overwrite data sets with exact names. *get_kegg* checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can of course generate 'same-day/same-version'
data sets in different directories if they so choose.
